%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Invoice Template
% LaTeX Template
% Version 1.0 (3/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the invoice.cls file to be in the same directory as
% the .tex file. The invoice.cls file provides the style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	DOCUMENT CONFIGURATION
%----------------------------------------------------------------------------------------

\documentclass{invoice} % Use the custom invoice class (invoice.cls)
\usepackage{parallel}
\usepackage[english,ukrainian]{babel}
\usepackage[utf8]{inputenc}

\def \tab {\hspace*{3ex}} % Define \tab to create some horizontal white space

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADING SECTION
%----------------------------------------------------------------------------------------

\hfil{\Huge\bf Initech Inc.}\hfil % Company providing the invoice
\bigskip\break % Whitespace
\hrule % Horizontal line

123 Broadway \hfill (000) 111-1111 \\ % Your address and contact information
City, State 12345 \hfill john@smith.com
\\ \\
{\bf Invoice To:} \\
\tab James Smith \\ % Invoice recipient
\tab Generic Corporation \\ % Recipient's company

{\bf Date:} \\
\tab \today \\ % Invoice date

%----------------------------------------------------------------------------------------
%	TABLE OF EXPENSES
%----------------------------------------------------------------------------------------
\begin{invoiceTable}

% \feetype{Consulting Services} % Fee category description

\hourrow{October 3, 2012}{8}{12} % Each separate billing day includes the date, the number of hours and the hourly rate
\hourrow{October 4, 2012}{6.5}{12}
\hourrow{October 5, 2012}{5.25}{12}
\hourrow{October 10, 2012}{9.75}{20}
\hourrow{October 11, 2012}{5}{12.51}

%------------------------------------------------

% \feetype{Accounting Services} % Fee category description

\hourrow{October 10, 2012}{2}{80}
\hourrow{October 11, 2012}{1}{80}

% \subtotal % Prints a subtotal, can be used multiple times

%------------------------------------------------

% \feetype{Hosting Expenses} % Fee category description

% \feerow{Web Hosting: October, 2012}{60} % A flat fee service, note there is no hourly rate for this

\end{invoiceTable}
% 
% Sum spelled out: \spellout{cost}{USD}

{\tiny\begin{Parallel}[c]{0.47\textwidth}{0.47\textwidth}
\selectlanguage{english}
\ParallelLText{All charges of correspondent banks are at the Supplier’s expenses.}
\selectlanguage{ukrainian}
\ParallelRText{Усі комісії банків-кореспондентів сплачує виконавець.}
\ParallelPar\vskip 1mm

\selectlanguage{english}
\ParallelLText{Payment hereof at the same time is the evidence of the work performance and the service delivery in full scope, acceptation thereof in full scope and the confirmation of final mutual installments between Parties.}
\selectlanguage{ukrainian}
\ParallelRText{Оплата згідно цього Інвойсу одночасно є свідченням виконання робіт та надання послуг в повному обсязі, їх прийняття, а також підтвердженням кінцевих розрахунків між Сторонами.}
\ParallelPar\vskip 1mm

\selectlanguage{english}
\ParallelLText{The Parties shall not be liable for non-performance or improper performance of the obligations under the agreement during the term of insuperable force circumstances.}
\selectlanguage{ukrainian}
\ParallelRText{Сторони звільняються від відповідальності за невиконання чи неналежне виконання зобов’язань за договором на час дії форс-мажорних обставин.}
\ParallelPar\vskip 1mm

\selectlanguage{english}
\ParallelLText{Payment according hereto shall be also the confirmation that Parties have no claims to each other and have no intention to submit any claims.}
\selectlanguage{ukrainian}
\ParallelRText{Оплата згідно цього Інвойсу є підтвердженням того, що Сторони не мають взаємних претензій та не мають наміру направляти рекламації.}
\ParallelPar\vskip 1mm

\selectlanguage{english}
\ParallelLText{Any disputes arising out of the agreement between the Parties shall be settled by the competent court at the location of a defendant.}
\selectlanguage{ukrainian}
\ParallelRText{Всі спори, що виникнуть між Сторонами по  угоді будуть розглядатись компетентним судом замісцезнаходження відповідача.}

\end{Parallel}}

%----------------------------------------------------------------------------------------

\end{document}
